Anomalous waves triggered by abrupt depth changes: laboratory experiments and truncated KdV statistical mechanics

### 2020-05-04 paper2_JNLS/Referee Reports/Ref2Response/Ref2.tex
NM

% COMMENT 2
\noindent
\comment{On Pg 5 Ln 44, it is said that "the location of the peak is the same for skewness and kurtosis and appears insensitive to driving amplitude". Can you elaborate on "appears" to say whether it is or not?}

>>>>

% COMMENT 2
\noindent
\comment{On Pg 5 Ln 44, it is said that ``the location of the peak is the same for skewness and kurtosis and appears insensitive to driving amplitude''. Can you elaborate on "appears" to say whether it is or not?}

### 2020-05-04 paper2_JNLS/paper.tex
NM

\author{
M.~N.~J.~Moore\thanks{Florida State University}, 
C.~Tyler Bolles\thanks{University of Michigan},
Andrew J.~Majda\thanks{Courant Institute of Mathematical Sciences}, 
Di Qi\footnotemark[3] }
\maketitle

@@

	Visual differences between the upstream and downstream dynamics are apparent in Fig.~\ref{trajectories}. The upstream trajectory shows several waves of modest amplitude all propagating leftward. Here, the magnitude of the positive and negative displacements are comparable. This is in stark contrast to the downstream dynamics, which feature fewer waves of larger amplitude propagating in either direction. In particular, one large wave is seen to propagate from the lower-left corner of the figure to the upper right. A bias towards positive surface displacement is apparent in these downstream dynamics, without even viewing the histograms.

>>>>

\author{
M.~N.~J.~Moore\thanks{United States Naval Academy}, 
C.~Tyler Bolles\thanks{University of Michigan},
Andrew J.~Majda\thanks{Courant Institute of Mathematical Sciences}, 
Di Qi\footnotemark[3] }
\maketitle

@@

	Visual differences between the upstream and downstream dynamics are apparent in Fig.~\ref{trajectories}. The upstream trajectory shows several waves of \new{moderate} amplitude all propagating leftward. Here, the magnitude of the positive and negative displacements are comparable. This is in stark contrast to the downstream dynamics, which feature fewer waves of larger amplitude propagating in either direction. In particular, one large wave is seen to propagate from the lower-left corner of the figure to the upper right. A bias towards positive surface displacement is apparent in these downstream dynamics, without even viewing the histograms.
